Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-02-02 main.tex
Last comments for now

{\em Hyperproperties}, i.e. properties of pairs\leo{sets?} of
execution traces, are the standard way of expressing security
properties\cn. In particular, {\em noninterference} is commonly
phrased as such a property: given two system states that seem
identical to an observer with low clearance, their execution traces
should also be indistinguishable\cn.

@@

The {\em underlying} step function, $\mathord{\stepstounderfull} \in \MACHS
\rightarrow \MACHS$, embodies the standard RISC-V ISA semantics.

>>>>

{\em Hyperproperties}, i.e. properties of pairs\leo{sets?} of
execution traces\footnote{\bcp{I'm not certain we're using the word
    correctly.  E.g., ``A hyperproperty is a set of properties [Clarkson and Schneider 2008, 2010]''}}, are the standard way of expressing security
properties\cn. In particular, {\em noninterference} is commonly
phrased as such a property: given two system states that seem
identical to an observer with low clearance, their execution traces
should also be indistinguishable\cn.

@@

The {\em underlying} step function,
$\mathord{\stepstounderfull} \in \MACHS \rightarrow \MACHS$, embodies the
standard RISC-V ISA semantics.  \bcp{It's probably clearer not to put RISCV
  in the notation---for most of the paper, the fact that it's a RISCV really
  doesn't matter.  Moreover, I think we want to make it a partial function,
  for simplicity of definitions in this part, and if we insist on RISCV here
  this will confuse people that know it doesn't have a HALT instruction.}
